### 2012-12-04 inst/examples/policycosts/writeup.Rmd

```{r cache-options, include=FALSE}
opts_chunk$set(cache=TRUE, cache.path="figure4/")
```

@@

```{r graphing-options, include=FALSE}
#opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"),
               tidy=FALSE, comment=NA, message=FALSE)
theme_notebook <- theme_grey() + 
                  theme(plot.background = 
                          element_rect(fill = "transparent",colour = NA),
                        panel.grid.minor = 
                          element_line(colour = "transparent"))
theme_set(theme_notebook)
```

@@

```{r}
source("fig4_helper_fun.R")
frac_lost <- seq(0,1, length=5)
out <- lapply(frac_lost, fig4, ls())
out <- melt(out)
colnames(out) = c("statistic", "penalty", "value", "index")
out <- cbind(out[1:3], fraction = frac_lost[out$index])
Figure4 <- ggplot(out) + geom_line(aes(fraction, value, col=penalty)) + facet_wrap(~statistic)
Figure4
````

>>>>

```{r cache-options, include=FALSE}
opts_chunk$set(cache=TRUE, cache.path="writeup/")
```

@@

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"),
               tidy=FALSE, comment=NA, message=FALSE)
theme_notebook <- theme_grey() + 
                  theme(plot.background = 
                          element_rect(fill = "transparent",colour = NA),
                        panel.grid.minor = 
                          element_line(colour = "transparent"))
theme_set(theme_notebook)
```

@@

```{r Figure4}
frac_lost <- seq(0.1,0.9, length=5)
out <- lapply(frac_lost, pdgControl:::fig4, ls())
out <- melt(out)
colnames(out) = c("statistic", "penalty", "value", "index")
out <- cbind(out[1:3], fraction__npv_lost = frac_lost[out$index])
Figure4 <- ggplot(out) + geom_point(aes(fraction_npv_lost, value, col=penalty)) + geom_line(aes(fraction, value, col=penalty)) + facet_wrap(~statistic, scales="free_y")
Figure4
````
